### 2022-02-09 paper/localpsf.tex
mass matrix causing negative numbers. Lumped mass no problems. Possible scaling or conditioning issue with big domain

@@

\section*{Acknowledgments}
We thank J.J. Alger, Longfei Gao, Mathew Hu, and Rami Nammour for helpful discussions.

>>>>

\begin{itemize}
	\item Stokes Krylov convergence (10 solves for nonlinear forward + 6 hessian matvecs for ellipsoid estimation + 10 matvecs for impulse responses + 30 matvecs for PCH6 CG solve + 100 matvecs for Reg CG solve)
	\item Stokes error vs num batches (small number of batches; 1, 3, 6, 9 batches?) (50 matvecs for randomized error estimation +)
	\item Velocity field
	\item Basal friction field
	\item Picture of impulse responses
	\item Mesh negative numbers picture
\end{itemize}

@@

\section*{Acknowledgments}
We thank J.J. Alger, Longfei Gao, Mathew Hu, and Rami Nammour for helpful discussions. Georg Stadler (domain geometry help)
